What We Eval in the Shadows

### 2021-04-17 paper/main.tex
intro

\vspace{2mm}\noindent\emph{Why do we Eval?} {\bf A short summary of the
results should go here.}

>>>>

\vspace{2mm}\noindent\emph{Why do we Eval?} The results of our study suggest
that \eval is widely used for the implementation of the language, and in many
libraries. End-user code makes less frequent and less sophisticated use of
\eval. In many ways, \eval in R is as bad as it gets: it's varied, performs
side-effects and reaches to many environments. By large, the motivations for
\eval relate to various forms of language extensions and meta-programming. \Eval
is used where other languages would provide macros. But, the expressive power of
\eval is higher as it can reach arbitrarily far back in the call stack.
